\MakeUppercase{Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-17 k-planar.tex
Resolving undefined references

    \item $\ell\le k+1$.
  \end{compactenum}
  We call any walk with properties (i)--(iv) a \emph{$\delta$-walk}. Therefore, to upper-bound $|B_x|$, it suffices to upper-bound the number of $\delta\in\{0,\ldots,d-1\}$ such that there exists a $\delta$-walk.  This is our goal for the remainder of this proof.

@@

  Apply \lemref{make-planar} to $G^{++}$ to obtain the set $Z\subseteq V(G^{++})$, the planar graph $G^*$, and the BFS spanning tree $T^*$ rooted at $r^*$.  For each edge $vw\in E(G)$, let $W_{vw}$ be the corresponding walk in $G^+$. The set $Z$ contains vertices in $V(G)$ as well as dummy vertices in $V(G^+-G)$. Create a new set $Z'\subseteq V(G)$ as
  \[
     Z' = \{ v : V(W_{vw})\cap Z\neq\emptyset \} \enspace .
  \]
  \note{PM}{We can certainly save a factor of 2 here because we only need one endpoint of each $vw$ that crosses $Z$ to take part in $Z'$.}
  Since $|Z\cap V_i| \le 2g$, the same argument used in the proof of \lemlabel{width-of-g-plus} shows that $|Z'\cap V_i|\le 2g\times 4\times (2k+1) = 16gk+8g$ for all $i\in\{1,\ldots,h\}$.

>>>>

    \item $\ell\le k+1$.
  \end{compactenum}
  We call any walk with properties (i)--(iv) a \emph{$\delta$-walk}. Therefore, to upper-bound $|B_x|$, it suffices to upper-bound the number of $\delta\in\{0,\ldots,d\}$ such that there exists a $\delta$-walk.\footnote{To account for the fact that $B_x$ contains $x$ we count $\delta=d$.  A $d$-walk corresponds, for example, to a 0-length walk that begins and ends at any vertex $v_0\in V(N_x-F_x)$.}  This is our goal for the remainder of this proof.

@@

  Apply \lemref{make-planar} to $G^{++}$ to obtain the set $Z\subseteq V(G^{++})$, the planar graph $G^*$, and the BFS spanning tree $T^*$ rooted at $r^*$.  For each edge $vw\in E(G)$, let $W_{vw}$ be the corresponding walk in $G^+$. The set $Z$ contains vertices in $V(G)$ as well as dummy vertices in $V(G^+-G)$. Create a new set $Z'\subseteq V(G)$ as
  \[
     Z' = \{ v : V(W_{vw})\cap Z\neq\emptyset \} \enspace .
  \]
  \note{PM}{We can certainly save a factor of 2 here because we only need one endpoint of each $vw$ that crosses $Z$ to take part in $Z'$.}
  Since $|Z\cap V_i| \le 2g$, the same argument used in the proof of \clmref{width-of-g-plus} shows that $|Z'\cap V_i|\le 2g\times 4\times (2k+1) = 16gk+8g$ for all $i\in\{1,\ldots,h\}$.
